Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-20 Paper/grass.tex
Compilation of an older version of the tex file to generate PDF
Changed Mahesh's name and institutional affiliation to preferred format

\documentclass[aps,prl,reprint,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1}  % for review and submission
%\documentclass[aps,twocolumn,floatfix,prl,10pt]{revtex4-1}
%\documentclass[letterpaper,10pt,prl,twocolumn,aps]{revtex4-1}
%\documentclass[aps,preprint,floatfix,prl]{revtex4-1}

@@

\begin{document}
\title{Linear instability underlying synchronous waving of marine grass in flow}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
\author{L. Mahadevan}
\affiliation{Harvard University, Cambridge MA 02138 USA}
\author{Mahesh Bandi\thanks{work performed while visiting Brown University}}
\affiliation{Okinawa Institute of Science and Technology, Okinawa, Japan}
\author{Amala Mahadevan}
\affiliation{Woods Hold Institute of Oceanography, Woods Hole MA USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}

>>>>

\documentclass[aps,prl,twocolumn,superscriptaddress,10pt]{revtex4-1}  % for review and submission
%\documentclass[aps,twocolumn,floatfix,prl,10pt]{revtex4-1}
%\documentclass[letterpaper,10pt,prl,twocolumn,aps]{revtex4-1}
%\documentclass[aps,preprint,floatfix,prl]{revtex4-1}

@@

\begin{document}
\title{Linear instability underlying synchronous waving of marine grass in flow}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
\author{L. Mahadevan}
\affiliation{Harvard University, Cambridge MA 02138 USA}
\author{M. M. Bandi\thanks{work performed while visiting Brown University}}
\affiliation{Collective Interactions Unit, OIST Graduate University, 1919-1 Tancha, Onna-son, Okinawa, Japan 904-0495}
\author{Amala Mahadevan}
\affiliation{Woods Hold Institute of Oceanography, Woods Hole MA USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}
